\section{Engineering section}
\subsection{Concept of robot}
\subsubsection{Construction}
\begin{itemize}
	\item Robot should be mobile, move quickly, and, if possible, in all four directions.
	\item Robot should have four sensors of angle (encoders) to use in the autonomous period.
	\item Robot should be compact not fill too much space, since it shouldn't hinder allies.
	\item Robot must be able to monitor all five (5) goals simultaneously. 
	\item The robot must have a special device for moving the movable baskets.
	\item If possible, the robot should be lightweight. It will be easier to carry.
	\item The construction of the robot should allow for quick change of some parts.
\end{itemize}
\subsubsection{Autonomous period}
\begin{itemize}
	\item Robot should have different versions of the autonomous period and use them depending on the ally's capabilities, its start place, and other conditions.
	\item The autonomous period program should be simple.
\end{itemize}
\subsubsection{Driver-controlled period}
\begin{itemize}
	\item Robot control should be simple and convenient
	\item One operator is fully responsible for the movement of the robot, the other for all another functions.
	\item Some steps in the controlled period may be implemented independently to help the operator.
	\item Operator should control speed of robot, since the robot should be able to perform precise manipulation.
\end{itemize}
\fillpage

\subsection{Strategy} 
\subsubsection{Autonomous period}
\begin{enumerate}
    \item Put two balls in two different baskets.
	\item Take the maximum number of mobile baskets and place them next to the parking area.
	\item On the way to the parking area, the mechanism of ball release should be activated.
	         
\end{enumerate}
\subsubsection{Driver-controlled period - main part}
\begin{enumerate}
	\item Allow our ally free access to the moving baskets. But, at the same time, it should carry one basket, because we have to save time.
	\item First the 90-cm basket should be filled with balls, then the 60-cm one and 30-cm one.
	\item Avoid collisions with ally and opponents, it is a waste of time.
\end{enumerate}
\subsubsection{Driver-controlled period - final}
\begin{enumerate}
	\item Fill the central basket with balls.
	\item Place maximum possible number of mobile baskets on the ramp.
	\item Call the robot to the ramp. 
\end{enumerate}
\fillpage

\subsection{Planned steps for creating of the robot}
\begin{enumerate}
	\item Creating a wheel (or track) base of the robot.
	\item Writing a program for controlling the wheelbase through one (1) joystick.
	\item Creating a system of goal control.
	\item Writing a programm for robot control through two (2) joysticks.
	\item Writing a programm for the autonomous period.
	\item Creating additional decorative elements.
	\item Installating protection elements on the robot to prevent damage during an accidental collision.
	\item Trainings (alone or with another robots).
	\item Making improvements on the based on preformance in first competition.
\end{enumerate}
\fillpage
