\subsubsection{23.01.2016}
\textit{\textbf{Time frame:}} 17:00-22:30 

This day our community organised a private competition on our own field. There were 3 teams including ours. There were held several matches 2 vs 1, which were played according to the entire game rules. This event provided teams with an experience of a true gameplay and allowed to test all the systems of the robots. It also was a source to find mistakes in construction and understand what should be improved in it.

During the competition, there were introduced some changes of the construction.

Firstly, the servo on the mechanism for grasping the hurdle was changed from standard to continious rotation. This was made to increase it's reliability. The continious rotation servo doesn't keep the angle, so it doesn't break down if the external force changes this angle. It is important feature, because, when the hooks are adjusting to the hurdle, the servo can be turned by the outer force.

Secondly, the ends of the hooks were wrapped by the tape to prevent the damage of the field or other robots by the sharp corners.

Into the driving-control program there was added a function for operating the mechanism for scoring alpinists inti the shelter. During the matches, this mechanism was tested.

It was decided to put the brushes on the gripper into a position, when they rotate in the same phases to find out, if this will be more effective, or not. The practice showed, that this position of brushes is unconvenient.

During the games it was found out, that the robot has plenty of areas, where the debris can get stuck, increasing our posession of it. These areas were aside the ramp for debris and under the bucket. The second area was temporarily covered by plates so as to prevent cubes from getting stuck in it.

At the mechanism for shifting the bucket it was revealed, that the cables, which pull the moving part, often get behind the pins, which causes the inability of shifting the trolley to the corner. This problem should be solved.

It was found out, that it is nit possible to collect more than 4 cubes into a bucket in game conditions. The problem was that cubes didn't settle down in a bucket as it was expected.
