\subsection{Experience that we got this year}
\begin{enumerate}
	\item This year we started build robot by next strategy. At first to discuss a concept then divide robot on modules and each person do one module. It is faster than if everyone do everything because working with each module performs parallel. So we need to continue follow this strategy.
	\item Also during elaborating modules developer must contact with each other in order to dock different modules. In addition it is necessary to hold meetings where we discuss progress in working on each module.
	\item In addition we need to assemble test modules as fast as possible in order to understand how this module will work and what problems can appear. So at first we need to make a approximate model and after that assemble it and test. After the tests to correct model in accordance with results of tests. Then to make a final version and test it.
	\item Also in the beginning of this year we had two teams. Each team made different robot. One robot is simple and maybe not able to perform all tasks but it is reliable and do it's tasks very fast. The second robot is more complex but it is able to do everything. This strategy is very profitable. When both robots play in one alliance they are very successful because they complement each other.
	\item It is important that robot must do minimal count of movings of it's body. For example this year we planned that simple robot will ride to middle zone (so we don't need a long lift in order to score to high goal) and turn to goal by body (so we don't need mechanism that turn bucket with debris to side). But it was turned out that it is very hard to ride to the middle zone and turn on mountain. So we had to add mechanisms that weren't taken in account in the basic concept. Due to it the construction of the robot became more complex and less reliable.
	\item In addition during the competition FTC Russia Open we paid attention that a lot of Russian teams that were strong 2 - 3 years ago can't compete with us now. We thought that it is because people who had a lot of experience and moved team forward stopped do FTC and new people haven't an experience and can't create very good robot. So we decided to make something like a book where described our experience. For example modules that are good for any task, (types of grippers, lifts, wheel bases) their pluses and minuses. So our experience will be transmitted to new people.  
\end{enumerate}