\addtocounter{number_of_meeting}{1}
\subsubsection{\arabic{number_of_meeting} Meeting}
	\textit{\textbf{Time frame:}} 22.09.2015 17:00-21:00 \newline
	\textit{\textbf{Preview:}} To put a priorities during the building robot and performing tasks of the game.\newline \newline
  
  \newline
  \textit{\textbf{Detailed explaination:}}
  \begin{enumerate*}
  	\item The tasks which robot must complete (We assume that robot can do everything. Tasks located in order of priority) :
  	\begin{enumerate}
  		\item Autonomous period:
  		\begin{enumerate}
  			\item Push the button and score climbers.
  			\item Ride to opposite mountain and collect balls and bricks.
  			\item Go to middle or high zone of the mountain.
  		\end{enumerate}
  		\item Driver control period:
  		\begin{enumerate}
	  		\item Put elements that we collected in autonomous period to the top box.
	  		\item Go from the mountain and collect 5 bricks.
	  		\item Put 5 bricks to the top box.
	  		\item Collect and put 5 bricks to the middle box.
	  		\item Score climbers.
	  		\item Turn clear signal.
	  		\item Pullup.
  		\end{enumerate}
  	\end{enumerate}
  	\item Implementation of robot that can perform next tasks (tasks are in order of priority)
  	\begin{enumerate}
  		\item Stable scoring to the middle box.
  		\item Scoring the climbers in driver control period.
  		\item Scoring climbers in autonomous period.
  		\item Riding to the high zone.
  		\item Pulling.
  		\item Turning clear signal.
  		\item Pushing button.
  	\end{enumerate}
	\newline
	
	Task for the next meeting: to elaborate concept of the simple robot.
  	
  \end{enumerate*}
  

  


\fillpage
